Incentivizing Exploration with Unbiased History

### 2018-11-02 model.tex
add a citation

%!TEX root = main.tex
\section{Model and Preliminaries}
\label{sec:model}
We study the multi-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents. There is a set $\A$ of $K$ possible actions, a.k.a. \emph{arms}. At each round $t\in [T]$, a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal. The reward from pulling an arm $a\in \A$ is drawn independently from Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$. An agent does not observe anything from the previous rounds, other than the message $m_t$. The problem instance is defined by (known) parameters $K,T$ and the (unknown) tuple of mean rewards, $(\mu_a:\,a\in\A)$. We are interested in \emph{regret}, defined as
\begin{align}\label{eq:intro-regret-defn}
\textstyle
  \reg(T)
  %= \reg(a_1, \ldots , a_T)
  = T \max_{a\in \A} \mu_a -
  \sum_{t\in [T]} \E[\mu_{a_t}].
\end{align}
(The expectation is over the chosen arms $a_t$, which depend on randomness in rewards, and possibly in the algorithm.)
The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret. We assume that mean rewards are bounded away from $0$ and $1$, to ensure sufficient entropy in rewards. For concreteness, we posit
    $\mu_a\in [\tfrac13,\tfrac23]$.

@@

%If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

>>>>

%!TEX root = main.tex
\section{Model and Preliminaries}
\label{sec:model}
\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.

We study the multi-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents. There is a set $\A$ of $K$ possible actions, a.k.a. \emph{arms}. At each round $t\in [T]$, a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal. The reward from pulling an arm $a\in \A$ is drawn independently from Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$. An agent does not observe anything from the previous rounds, other than the message $m_t$. The problem instance is defined by (known) parameters $K,T$ and the (unknown) tuple of mean rewards, $(\mu_a:\,a\in\A)$. We are interested in \emph{regret}, defined as
\begin{align}\label{eq:intro-regret-defn}
\textstyle
  \reg(T)
  %= \reg(a_1, \ldots , a_T)
  = T \max_{a\in \A} \mu_a -
  \sum_{t\in [T]} \E[\mu_{a_t}].
\end{align}
(The expectation is over the chosen arms $a_t$, which depend on randomness in rewards, and possibly in the algorithm.)
The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret. We assume that mean rewards are bounded away from $0$ and $1$, to ensure sufficient entropy in rewards. For concreteness, we posit
    $\mu_a\in [\tfrac13,\tfrac23]$.

@@

\jmcomment{Should we emphasize heterogeneity here?}
%If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
